---
title: "1. Neighborhood name list and Flashback Data"
author: "Lijun Peng"
date: "24/5/2022"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Library
```{r}
library(tibble)
library(dplyr)
library(qdap)
library(tidytext)
library(tm)
library(ggplot2)
library(tidyverse)
library(sp)
library(sf)
library(rnaturalearth)
library(rgeos)
library(rgdal)
library(osmar)
library(osmdata)
library(knitr)
library(kableExtra)
library(lubridate)
```

Extract neighborhood name from OpenStreetMap #####

# Import RegSO shapefile
```{r}
library(sf)
deso_geo <- st_read("D:/Nutstore no sync files/233-LIU/233.15-Master Thesis/GIS data/deso_2018_2021-10-21/DeSO_2018_v2.gpkg")
reso_geo <- st_read("D:/Nutstore no sync files/233-LIU/233.15-Master Thesis/GIS data/regso_2018_v1_20211103/RegSO_2018_v1.gpkg")
```
# Check RegSO shapefile properties
```{r}
# Checking properties
class(deso_geo)
dim(deso_geo)
#dataonly_deso <- st_drop_geometry(deso_geo)
st_geometry_type(deso_geo)
st_crs(deso_geo)
st_bbox(deso_geo)
getClass("Spatial")

dim(deso_geo_Stkh)
length(unique(deso_geo_Stkh$deso))
```
# Get Stockholm neighborhood names from OSM, suburb
```{r}
# The definition of "suburb" is: "A part of a town or city with a well-known name and often a distinct identity."
# So I only select "suburb"

stkh_osm_suburb <- opq(bbox = "Stockholm County (54391)") %>% 
  add_osm_feature(key = "place", value = c("suburb")) %>% 
  osmdata_sf()

Encoding(stkh_osm_suburb$osm_points$name) <- "UTF-8"
Encoding(stkh_osm_suburb$osm_lines$name) <- "UTF-8"
Encoding(stkh_osm_suburb$osm_polygons$name) <- "UTF-8"
Encoding(stkh_osm_suburb$osm_multipolygons$name) <- "UTF-8"

stkh_osm_suburb_points <- tibble(unique(na.omit(stkh_osm_suburb$osm_points$name)))
colnames(stkh_osm_suburb_points) <- "name"

stkh_osm_suburb_lines <- tibble(unique(na.omit(stkh_osm_suburb$osm_lines$name)))
colnames(stkh_osm_suburb_lines) <- "name"

stkh_osm_suburb_polygons <- tibble(unique(na.omit(stkh_osm_suburb$osm_polygons$name)))
colnames(stkh_osm_suburb_polygons) <- "name"

stkh_osm_suburb_multipolygons <- tibble(unique(na.omit(stkh_osm_suburb$osm_multipolygons$name)))
colnames(stkh_osm_suburb_multipolygons) <- "name"

# There variable has 215 names
stkh_osm_suburb_names <- stkh_osm_suburb_points %>% 
  bind_rows(stkh_osm_suburb_lines, stkh_osm_suburb_polygons, stkh_osm_suburb_multipolygons) %>% 
  unique()
```
# Export OSM neighborhood name list
```{r}
osm_neighbor_names <- write.table(stkh_osm_suburb_names, file = "D:/Nutstore no sync files/233-LIU/233.15-Master Thesis/Neighborhood names/osm_suburb_names.txt", fileEncoding = "UTF-8")
```
# Check OSM map division: suburb + neighbourhood
```{r}
stkh_osm <- opq(bbox = "Stockholm County (54391)") %>% 
  add_osm_feature(key = "place", value = c("suburb","neighbourhood")) %>% 
  osmdata_sf()

Encoding(stkh_osm$osm_points$name) <- "UTF-8"
Encoding(stkh_osm$osm_lines$name) <- "UTF-8"
Encoding(stkh_osm$osm_polygons$name) <- "UTF-8"
Encoding(stkh_osm$osm_multipolygons$name) <- "UTF-8"

stkh_osm_points <- tibble(unique(na.omit(stkh_osm$osm_points$name)))
colnames(stkh_osm_points) <- "name"

stkh_osm_lines <- tibble(unique(na.omit(stkh_osm$osm_lines$name)))
colnames(stkh_osm_lines) <- "name"

stkh_osm_polygons <- tibble(unique(na.omit(stkh_osm$osm_polygons$name)))
colnames(stkh_osm_polygons) <- "name"

stkh_osm_multipolygons <- tibble(unique(na.omit(stkh_osm$osm_multipolygons$name)))
colnames(stkh_osm_multipolygons) <- "name"

# There variable has 339 names
stkh_osm_names <- stkh_osm_points %>% 
  bind_rows(stkh_osm_lines, stkh_osm_polygons, stkh_osm_multipolygons) %>% 
  unique()

# Export OSM neighborhood name listo< suburb + neighborhood
name_suburb_neigh <- write.csv(stkh_osm_names, "D:/Nutstore no sync files/233-LIU/233.15-Master Thesis/GIS data/name_suburb_neigh.txt", fileEncoding = "UTF-8")
```
# Check OSM map division: "city","borough","suburb","quarter","neighbourhood", "city_block"
```{r}
# It's unnecessary to check "region, district and municipality" level. The result is " $osm_points : 'sf' Simple Features Collection with 31 points". I already have the municipalities names.
stkh_osm_1 <- opq(bbox = "Stockholm County (54391)") %>%
  add_osm_feature(key = 'place', value = c("region","district", "municipality")) %>%
  #add_osm_feature(key = 'place', value = 'municipality') %>%
  osmdata_sf()
na.omit(stkh_osm_1$osm_points$name)
#===============================================================================
stkh_osm_2 <- opq(bbox = "Stockholm County (54391)") %>% 
  add_osm_feature(key = "place", value = c("city","borough","suburb","quarter","neighbourhood", "city_block")) %>% 
  osmdata_sf()

Encoding(stkh_osm_2$osm_lines$name) <- "UTF-8"
Encoding(stkh_osm_2$osm_polygons$name) <- "UTF-8"
Encoding(stkh_osm_2$osm_multipolygons$name) <- "UTF-8"

stkh_osm_2_lines <- tibble(unique(na.omit(stkh_osm_2$osm_lines$name)))
colnames(stkh_osm_2_lines) <- "name"

stkh_osm_2_polygons <- tibble(unique(na.omit(stkh_osm_2$osm_polygons$name)))
colnames(stkh_osm_2_polygons) <- "name"

stkh_osm_2_multipolygons <- tibble(unique(na.omit(stkh_osm_2$osm_multipolygons$name)))
colnames(stkh_osm_2_multipolygons) <- "name"

# There variable has 3,342 names
stkh_osm_2_names <- stkh_osm_2_lines %>% 
  bind_rows(stkh_osm_2_polygons, stkh_osm_2_multipolygons) %>% 
  unique()
#===============================================================================
# "town","village","hamlet"

stkh_osm_3 <- opq(bbox = "Stockholm County (54391)") %>% 
  add_osm_feature(key = "place", value = c("town","village","hamlet")) %>% 
  osmdata_sf()

Encoding(stkh_osm_3$osm_points$name) <- "UTF-8"
#Encoding(stkh_osm_3$osm_lines$name) <- "UTF-8"
Encoding(stkh_osm_3$osm_polygons$name) <- "UTF-8"
#Encoding(stkh_osm_3$osm_multilines$name) <- "UTF-8"

stkh_osm_3_points <- tibble(unique(na.omit(stkh_osm_3$osm_points$name)))
colnames(stkh_osm_3_points) <- "name"

stkh_osm_3_lines <- tibble(unique(na.omit(stkh_osm_3$osm_lines$name)))
colnames(stkh_osm_3_lines) <- "name"

stkh_osm_3_polygons <- tibble(unique(na.omit(stkh_osm_3$osm_polygons$name)))
colnames(stkh_osm_3_polygons) <- "name"

stkh_osm_3_multipolygons <- tibble(unique(na.omit(stkh_osm_3$osm_multipolygons$name)))
colnames(stkh_osm_3_multipolygons) <- "name"

# There variable has 82 names
stkh_osm_3_names <- stkh_osm_3_points %>% 
  bind_rows(stkh_osm_3_lines, stkh_osm_3_polygons, stkh_osm_3_multipolygons) %>% 
  unique()

```
# *Combine neighborhood name lists (Kommunnamn + RegSO + OSM)*
```{r}
combine_name <- read.csv("New name with kommunname.csv", encoding = "UTF-8")
combine_name_features <- combine_name %>% 
  count(X.U.FEFF.Kommunnamn, sort = T)
ggplot(data = combine_name_features, aes(y = reorder(X.U.FEFF.Kommunnamn, n), x = n)) + 
  geom_bar(stat = "identity") +
  scale_x_continuous(breaks = c(3,10,20,30,40,143)) +
  ggtitle("The distribution neighborhood names by county")
```
# *Import RegSO names (483)*
```{r}
# 483 regso names, after remove 39 names with multiple locations and with common meaning, this df has municipalities
regso_name_aggtdegso_ori <- read.csv(file = "D:/Nutstore no sync files/233-LIU/233.15-Master Thesis/SCB-demographic data/regso_names_wo_multi.csv", encoding = "UTF-8")
colnames(regso_name_aggtdegso_ori) <- c("kommun","regso","new_name")

# In this regso and new name list, 10 new names have multiple regso names, other names are the same in "regso" and "new_name", so use this list is used to aggregate regso names and regso demographical data.
# column "regso" has 483 unique regso names
# column "new_names" has 473 unique regso names, 10 of regso have new names
regso_name_aggtdegso <- regso_name_aggtdegso_ori %>% 
  select(-1)

# 483 names, this df can remove unwanted regso names
regso_aggname_only <- tibble(regso_name_aggtdegso_ori[,2])
colnames(regso_aggname_only) <- "regso"

```
# *Import neighborhood name list (709)*
```{r}
#RegSO + DeSO + OSM + FC6ramlingar + Utsatta omrC%den names
# 709 neighborhood names, full list
neighbor_namelist <- read.csv("D:/Nutstore no sync files/233-LIU/233.15-Master Thesis/Neighborhood names/New name with kommunname.csv", encoding = "UTF-8")
colnames(neighbor_namelist) <- c("Kommunnamn", "namelist")
#convert names to lowcase
neighbor_namelist$namelist <- tolower(neighbor_namelist$namelist)
```

Extract neighborhood post (Posts that include neighborhod names) #####

# *Extract posts that only contain neighborhood names*
## Import Flashback raw data by parts (The total posts have 13 GB)
```{r}
#Import Flashback data, home, society and lifestyle; hem : 3505126
hem_all <- read.csv("D:/Nutstore no sync files/233-LIU/233.15-Master Thesis/Flashback Data/hem.csv", encoding = "UTF-8")
#                nrows = 1000)
hem <- hem_all[,c(1,2,8)]

# livsstil: 802353
livsstil_all <- read.csv("D:/Nutstore no sync files/233-LIU/233.15-Master Thesis/Flashback Data/livsstil.csv", encoding = "UTF-8")
livsstil <- livsstil_all[,c(1,2,8)]

# samhC$lle: 9748101
samhalle_all <- read.csv("D:/Nutstore no sync files/233-LIU/233.15-Master Thesis/Flashback Data/samhalle.csv", encoding = "UTF-8")
samhalle <- samhalle_all[,c(1,2,8)]
samhalle1 <- samhalle_all[1:2500000,]
samhalle1_save <- write.csv(samhalle1,file = "D:/Nutstore no sync files/233-LIU/233.15-Master Thesis/Flashback Data/samhalle1_save.csv", fileEncoding = "UTF-8")

samhalle2 <- samhalle_all[2500001:5000000,]
samhalle2_save <- write.csv(samhalle2,file = "D:/Nutstore no sync files/233-LIU/233.15-Master Thesis/Flashback Data/samhalle2_save.csv", fileEncoding = "UTF-8")

samhalle3 <- samhalle_all[5000001:7500000,]
samhalle3_save <- write.csv(samhalle3,file = "D:/Nutstore no sync files/233-LIU/233.15-Master Thesis/Flashback Data/samhalle3_save.csv", fileEncoding = "UTF-8")

samhalle4 <- samhalle_all[7500001:9748101,]
samhalle4_save <- write.csv(samhalle4,file = "D:/Nutstore no sync files/233-LIU/233.15-Master Thesis/Flashback Data/samhalle4_save.csv", fileEncoding = "UTF-8")
```
## str_detect Function-- Exact match. Find posts that include neighborhood names exactly 
```{r}
extractrows2 <- function(neighborhood,flashback,post) {
  require(stringr)
  flashback[str_detect(as.character(flashback[[post]]),regex(paste("\\b",neighborhood,"\\b"), ignore_case = TRUE)),] %>% 
    bind_cols(name = neighborhood)
}
#test
# hem_test_sample <- hem[1:10,]
# test_ool <- extractrows2("Intressant",hem_test_sample,"posting_wo_quote")
# test_ool
```
## Due the big size of data, loop each dataset one after one. Loop livsstil
```{r}
livsstil_post <- lapply(as.character(neighbor_namelist$namelist),extractrows2,flashback=livsstil,post="posting_wo_quote")
livsstil_just_post_allv <- do.call(rbind.data.frame, livsstil_post)
livsstil_just_post <- livsstil_just_post_allv[,c(1,2,4,3)]
# save data. allv means all variables
livsstil_just_post_save <- write.csv(livsstil_just_post, file = "D:/Nutstore no sync files/233-LIU/233.15-Master Thesis/Flashback Data/livsstil_just_post_save.csv", fileEncoding = "UTF-8")
livsstil_just_post_save_allv <- write.csv(livsstil_just_post_allv, file = "D:/Nutstore no sync files/233-LIU/233.15-Master Thesis/Flashback Data/livsstil_just_post_save_allv.csv", fileEncoding = "UTF-8")
```
## loop hem
```{r}
hem_post <- lapply(as.character(neighbor_namelist$namelist),extractrows2,flashback=hem,post="posting_wo_quote")
hem_just_post <- do.call(rbind.data.frame, hem_post)
hem_just_post <- hem_just_post[,c(1,2,4,3)]
# save data
hem_just_post_save <- write.csv(hem_just_post, file = "D:/Nutstore no sync files/233-LIU/233.15-Master Thesis/Flashback Data/hem_just_post_save.csv", fileEncoding = "UTF-8")
```
## loop samhalle
```{r}
samhalle_post1 <- lapply(as.character(neighbor_namelist$namelist),extractrows2,flashback=samhalle1,post="posting_wo_quote")
samhalle_just_post11 <- do.call(rbind.data.frame, samhalle_post1)
samhalle_just_post1 <- samhalle_just_post11[,c(1,2,9,8)]
# save data
samhalle_just_post_save1 <- write.csv(samhalle_just_post1, file = "D:/Nutstore no sync files/233-LIU/233.15-Master Thesis/Flashback Data/samhalle_just_post_save1.csv", fileEncoding = "UTF-8")
samhalle_just_post_save1_allv <- write.csv(samhalle_just_post11, file = "D:/Nutstore no sync files/233-LIU/233.15-Master Thesis/Flashback Data/samhalle_just_post_save1_allv.csv", fileEncoding = "UTF-8")

# import data2
samhalle2 <- read.csv("D:/Nutstore no sync files/233-LIU/233.15-Master Thesis/Flashback Data/samhalle2_save.csv", encoding = "UTF-8")
samhalle_post2 <- lapply(as.character(neighbor_namelist$namelist),extractrows2,flashback=samhalle2,post="posting_wo_quote")
samhalle_just_post22 <- do.call(rbind.data.frame, samhalle_post2)
samhalle_just_post2 <- samhalle_just_post22[,c(2,3,10,9)]
# save data
samhalle_just_post_save2 <- write.csv(samhalle_just_post2, file = "D:/Nutstore no sync files/233-LIU/233.15-Master Thesis/Flashback Data/samhalle_just_post_save2.csv", fileEncoding = "UTF-8")
samhalle_just_post_save2_allv <- write.csv(samhalle_just_post22, file = "D:/Nutstore no sync files/233-LIU/233.15-Master Thesis/Flashback Data/samhalle_just_post_save2_allv.csv", fileEncoding = "UTF-8")

# import data3
samhalle3 <- read.csv("D:/Nutstore no sync files/233-LIU/233.15-Master Thesis/Flashback Data/samhalle3_save.csv", encoding = "UTF-8")
samhalle_post3 <- lapply(as.character(neighbor_namelist$namelist),extractrows2,flashback=samhalle3,post="posting_wo_quote")
samhalle_just_post33 <- do.call(rbind.data.frame, samhalle_post3)
samhalle_just_post3 <- samhalle_just_post33[,c(2,3,10,9)]
# save data
samhalle_just_post_save3 <- write.csv(samhalle_just_post3, file = "D:/Nutstore no sync files/233-LIU/233.15-Master Thesis/Flashback Data/samhalle_just_post_save3.csv", fileEncoding = "UTF-8")
samhalle_just_post_save3_allv <- write.csv(samhalle_just_post33, file = "D:/Nutstore no sync files/233-LIU/233.15-Master Thesis/Flashback Data/samhalle_just_post_save3_allv.csv", fileEncoding = "UTF-8")

# import data4
samhalle4 <- read.csv("D:/Nutstore no sync files/233-LIU/233.15-Master Thesis/Flashback Data/samhalle4_save.csv", encoding = "UTF-8")
samhalle_post4 <- lapply(as.character(neighbor_namelist$namelist),extractrows2,flashback=samhalle4,post="posting_wo_quote")
samhalle_just_post44 <- do.call(rbind.data.frame, samhalle_post4)
samhalle_just_post4 <- samhalle_just_post44[,c(2,3,10,9)]
# save data
samhalle_just_post_save4 <- write.csv(samhalle_just_post4, file = "D:/Nutstore no sync files/233-LIU/233.15-Master Thesis/Flashback Data/samhalle_just_post_save4.csv", fileEncoding = "UTF-8")
samhalle_just_post_save4_allv <- write.csv(samhalle_just_post44, file = "D:/Nutstore no sync files/233-LIU/233.15-Master Thesis/Flashback Data/samhalle_just_post_save4_allv.csv", fileEncoding = "UTF-8")
```
## conbine posts that contain neighborhood names among 3 sub-forums
```{r}
# livsstil
posts_livsstil <- read.csv("D:/Nutstore no sync files/233-LIU/233.15-Master Thesis/Flashback Data/livsstil_just_post_save.csv", encoding = "UTF-8")

# hem
posts_hem <- read.csv("D:/Nutstore no sync files/233-LIU/233.15-Master Thesis/Flashback Data/hem_just_post_save.csv", encoding = "UTF-8")

# samhC$lle
samhalle_post1 <- read.csv("D:/Nutstore no sync files/233-LIU/233.15-Master Thesis/Flashback Data/samhalle_just_post_save1.csv", encoding = "UTF-8")
samhalle_post2 <- read.csv("D:/Nutstore no sync files/233-LIU/233.15-Master Thesis/Flashback Data/samhalle_just_post_save2.csv", encoding = "UTF-8")
samhalle_post3 <- read.csv("D:/Nutstore no sync files/233-LIU/233.15-Master Thesis/Flashback Data/samhalle_just_post_save3.csv", encoding = "UTF-8")
samhalle_post4 <- read.csv("D:/Nutstore no sync files/233-LIU/233.15-Master Thesis/Flashback Data/samhalle_just_post_save4.csv", encoding = "UTF-8")

posts_samhalle <- rbind(samhalle_post1, samhalle_post2, samhalle_post3, samhalle_post4)

# combine all
posts_neighbor <- rbind(posts_livsstil, posts_hem, posts_samhalle)
posts_neighbor_save <- write.csv(posts_neighbor, file = "D:/Nutstore no sync files/233-LIU/233.15-Master Thesis/Flashback Data/posts_neighbor_save_3.csv", fileEncoding = "UTF-8")
```
# *Import selected posts (i.e., neighborhood-post)*
```{r}
# the data is posts that contain neighborhood names, one post can have several names, so 194,572 are not unique posts
posts_neighbor_all <- read.csv(file = "D:/Nutstore no sync files/233-LIU/233.15-Master Thesis/Flashback Data/posts_neighbor_save_3.csv", encoding = "UTF-8")

# Extract year
# library(lubridate)
posts_neighbor_all$date <- as_date(posts_neighbor_all$date)
posts_neighbor_all$year <- as.numeric(format(posts_neighbor_all$date,"%Y"))

# unique posts_neighbor, 149,864
posts_neighbor_all_uniq <- read.csv(file = "D:/Nutstore no sync files/233-LIU/233.15-Master Thesis/Flashback Data/posts_neighbor_all_uniq_save_3.csv", encoding = "UTF-8") %>% 
  select(-1)
```
# *Data process*
## 1. Descrip_data table
### 1.1 Total posts: Hem, bostad & familj + Livsstil + Society
### 1.2 Total posts that contains neighborhood names in Stockholm County
### 1.3 Number of neighborhood names
### 1.4 Number of neighborhood names that be mentioned
Table 2 Descriptive statistics for posts and neighborhood names
```{r}
#1. Total posts: Hem, bostad & familj + Livsstil + Samh??lle
Total_posts <- 3505126 + 802353 + 9748101
#2. Total posts that contains neighborhood names in Stockholm l??n
Total_select_posts <- length(unique(posts_neighbor_all$posting_wo_quote))
#3. Number of neighborhood names
Num_names <- length(neighbor_namelist$namelist)
#4. Number of neighborhood names that be mentioned
Num_mentioned_names <- length(unique(posts_neighbor_all$name))
#5. Number of RegSO names
#Num_regso <- length(unique(regso_aggname_only$regso))
Num_regso <- 522
#6. Number of final RegSO name
Num_agg_regso <- 473
# mention names in RegSO
Num_regso_mention <- 229

perc_post <- 100
perc_select <- as.integer(Total_select_posts/Total_posts * 100)
perc_name <- 100
perc_mentioned_name <- as.integer(Num_mentioned_names/Num_names * 100)
perc_regso <- 100
perc_agg_regso <- as.integer(Num_agg_regso/Num_regso * 100)
perc_mentioned_regso <- as.integer(Num_regso_mention/Num_regso * 100)

percs <- tibble( perc_select, perc_post, perc_mentioned_name, perc_name,
                perc_agg_regso, perc_mentioned_regso, perc_regso) %>% 
  pivot_longer(everything(), names_to = "Description", values_to = "Percentage (%)")
percs$Description <- c("Percent of selected posts",
                       NA,
                       "Percent of mentioned names",
                       NA,
                       "Percent of adjusted RegSO names",
                       "Percent of mentioned RegSO naems",
                       NA)

descrip_data <- tibble(Total_select_posts,Total_posts, Num_mentioned_names,Num_names, 
                       Num_agg_regso,Num_regso_mention,Num_regso) %>% 
  pivot_longer(everything(), names_to = "Post and name", values_to = "Number")
descrip_data$`Post and name` <- c("Selected posts","Total posts", "Mentioned names","Neighborhoods", "Adjusted RegSO names","Mentioned names in RegSO","RegSO")

name_descriptive_table <- cbind(descrip_data, percs)

#5. Descrip_data table
options(knitr.kable.NA = '')
name_descriptive_table <- replace(name_descriptive_table, name_descriptive_table==100, "")

flashback_table <- knitr::kable(name_descriptive_table, align = "lclc", digits = 0,
                             format.args = list(big.mark = ",", scientific = FALSE),
                             #caption = "Table 1 Neighborhood names descriptive statistics",
                             booktabs = T) %>% 
  kable_classic(full_width = F, html_font = "Cambria") %>% 
  kable_styling(latex_options = "hold_position") %>% 
  pack_rows("Post",1,2) %>% 
  pack_rows("Nieghborhood name",3,4) %>% 
  pack_rows("RegSO name",5,7) %>% 
  kableExtra::footnote(general = "Here are the sources of the data",
           number = c("souce: Posts come from a Swedish online open forum Flashback. Three sub-forums are included: a) Home, house and family (Hem,bostad & familj); b) Society (Samh??lle); and c) Lifestyle (livsstil)",
                    "Neighborhood names come from RegSo, OSM, F??rsamlingar and Utsatta omr??den.", 
                    "RegSo is Sweden regional statistical areas; OSM is the OpenStreetMap;", 
                    "F??rsamlingar is the church division in Sweden;", "Utsatta omr??den is vulnerable areas that listed by police, these places are characterized by a low socio-economic status and high crime rate.", 
                    "Adjusted RegSO names are RegSO names after remove names with genernal meaning and multiple locations."),
           fixed_small_size = TRUE, 
           footnote_as_chunk = TRUE, 
           threeparttable = F)  
knitr::kable(replace(flashback_table, flashback_table==100, ""))
flashback_table

```
## 2. The distribution of neighborhood names by kommun (county).
```{r}
name_freq_by_municipality <- neighbor_namelist %>% 
  count(Kommunnamn, sort = T) %>% 
  ggplot(aes(x = n, y = reorder(Kommunnamn, n))) +
  geom_bar(stat = "identity") +
  ggtitle("Figure 1 The distribution of neighborhood names by municipality") +
  xlab("Number of neighborhoods") +
  ylab("Kommun namn (Municipality name)") +
  theme_classic()
name_freq_by_municipality 
```
## 3. Aggregate selected posts by year
## Figure 1. Yearly total neighborhoods mentions on Flashback from 2000 to 2021 
```{r}
posts_neighbor_all_byyear <- posts_neighbor_all %>% 
  count(year)
#plot(posts_neighbor_all_byyear)

posts_neighbor_all_byyear_plot <- ggplot(posts_neighbor_all_byyear, aes(x = year, y = n)) +
  geom_line() +
  #ggtitle("Figure 2 The distribution of neighborhoods mentions by year") +
  xlab("Year") +
  ylab("Mentions") +
  scale_x_continuous(breaks = c(2000,2001,2002,2003,2004,2005,2006,2007,2008,2009,2010,2011,2012,2013,2014,2015,2016,2017,2018,2019,2020,2021)) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=0.2)) +
  labs(caption = "Source: Flashback posts")
ggsave("posts_neighbor_all_byyear_plot.png", width = 20, height = 10, units = c("cm"), dpi = 1000)

```
## 4. Display Flashback subtitles
Appendix 1.1. Flashback subtitles, forum: Home
Appendix 1.2. Flashback subtitles, forum: Lifestyle
Appendix 1.3. Flashback subtitles, forum: Society
```{r}
sbuforums_title <- read.csv(file = "D:/Nutstore no sync files/233-LIU/233.15-Master Thesis/Draft/figure_table_map/forums' titles.csv", encoding = "UTF-8")
colnames(sbuforums_title) <- c("Forums","Sub-forums","Frequency")
rownames(sbuforums_title) <- NULL

title_home <- knitr::kable(sbuforums_title[sbuforums_title$Forums == "Home",],
             format.args = list(big.mark = ",", scientific = FALSE), booktab = T) %>% 
                             #caption = "Table  Flashback subforum title") %>%
  kable_classic(full_width = F, html_font = "Cambria") %>%
  kable_styling(latex_options = "hold_position") %>% 
  kableExtra::footnote(general = "Source: Flashback posts",
           fixed_small_size = TRUE, 
           footnote_as_chunk = F, 
           threeparttable = F)


title_lifestyle <- knitr::kable(sbuforums_title[sbuforums_title$Forums == "Lifestyle",],
             format.args = list(big.mark = ",", scientific = FALSE), booktab = T) %>% 
                             #caption = "Table  Flashback subforum title") %>%
  kable_classic(full_width = F, html_font = "Cambria") %>%
  kable_styling(latex_options = "hold_position") %>% 
  kableExtra::footnote(general = "Source: Flashback posts",
           fixed_small_size = TRUE, 
           footnote_as_chunk = F, 
           threeparttable = F)


title_society <- knitr::kable(sbuforums_title[sbuforums_title$Forums == "Society",],
             format.args = list(big.mark = ",", scientific = FALSE), booktab = T) %>% 
                             #caption = "Table  Flashback subforum title") %>%
  kable_classic(full_width = F, html_font = "Cambria") %>%
  kable_styling(latex_options = "hold_position") %>% 
  kableExtra::footnote(general = "Source: Flashback posts",
           fixed_small_size = TRUE, 
           footnote_as_chunk = F, 
           threeparttable = F)

```